### 2012-06-01 FFI-Simulator/ffi-simulator.tex
la2pdf commit - 2012:06:01	14:29:30	(Fri 1.Jun)

\subsection{Using OpenGL only for the simulations?}

@@

Our original idea was to use OpenGL to produce depth-maps of the object and (optionally) the seafloor, and then use CUDA to compute how a sonar array would illuminate this scene. However, if we can treat sound as ``light'', we believe it to be better to use OpenGL simulate the entire scene and generate the required 2D views and perspectives of it. The advantage of doing ``everything'' in OpenGL is pretty obvious, we may then support whatever OpenGL supports with little extra effort. The gaming industry demands speed, so such a simulator should also be very fast.

@@

\begin{table}[H]\centering
\begin{tabular}[c]{l l l}\hline
\rowcolor{tabBlue}                  & CUDA/OpenGL    & OpenGL only \\\hline
Development time (estimate)         & 6 weeks        & 4 weeks     \\
Development complexity              & Moderate       & Low \\
Amount of code                      & More           & Less \\
Maintainability                     & Moderate       & Moderate \\
Code readability                    & Moderate       & Moderate \\
Signal model                        & Arbitrary      & Light rays  \\
Sound$\rightarrow$light calibration & Not necessary  & Necessary(?) \\
Multipath support                   & Possible       & Possible \\
Speckle support                     & Possible       & Hard \\
Diffraction support                 & Possible       & Hard \\
ATI/nVidia support                  & nVidia only    & Both \\
\end{tabular}
\vspace{5pt}\caption{Comparison of implementation approaches}\label{comparison}
\end{table}

@@

We propose using OpenGL to simulate the scene, and model the array as lightsources. This will make it unsuitable for simulating speckle and diffraction effects, but a ``simple'' simulator should probably not take such effects into account anyhow. Penetrable objects can be simulated in either case, although we are not sure whether the

>>>>

In addition we see that each approach shares the same initial steps. The risk of choosing an OpenGL-only implementation is therefore reduced, since we may easily switch to the CUDA implementation if an OpenGL prototype fails to produce the desired results.

\subsection{Using only OpenGL for the simulator?}

\begin{table}[b]\centering
\begin{tabular}[c]{l l l}\hline
\rowcolor{tabBlue}                  & CUDA/OpenGL    & OpenGL only \\\hline
Development time (per person)       & 6 weeks        & 4 weeks     \\
Development complexity              & Moderate       & Low \\
Amount of code                      & More           & Less \\
Maintainability                     & Moderate       & Moderate \\
Code readability                    & Moderate       & Moderate \\
Signal model                        & Arbitrary      & Light rays  \\
Sound$\rightarrow$light calibration & Not necessary  & Necessary(?) \\
Multipath support                   & Possible       & Possible \\
Speckle support                     & Possible       & Hard \\
Diffraction support                 & Possible       & Hard \\
Complex image                       & Easy           & Hard \\
ATI/nVidia support                  & nVidia only    & Both \\
\end{tabular}
\vspace{5pt}\caption{Comparison of implementation approaches}\label{comparison}
\end{table}

@@

Our original idea was to use OpenGL to produce depth-maps of the object and (optionally) the seafloor, and then use CUDA to compute how a sonar array would illuminate this scene. However, since were only interested in pixel intensities, and sound may be treated as ``light'' with reasonable accuracy, we believe that OpenGL can be used to simulate the entire scene. This way we may support whatever OpenGL supports with little extra effort. The gaming industry demands speed, so such a simulator should also be very fast.

The main advantage of the CUDA implementation lies in its flexibility. If desired, it can be modified to handle sound propagation in non-ideal mediums, penetrable objects, signal multipath, diffraction and phase-dependent effects such as speckle. However, this will also lead to increased code complexity and development time, and  will naturally increase. However, we expect that such features will be more realizable in CUDA than OpenGL.

@@

@@

We propose using OpenGL to simulate the scene, and model the array as lightsources. This will make it unsuitable for simulating speckle and diffraction effects, but a "simple'' simulator should probably not take such effects into account anyhow. Penetrable objects can be simulated in either case, although we are not sure whether the OpenGL framework can support this with ease. An OpenGL implementation will be highly portable, and believed to support the functionality needed to generate a good enough template image.

We aim to start development in July. The goal is to have an OpenGL prototype ready within a couple weeks, and from there decide which approach to go for. We propose monthly progress reports and meetings to discuss further 
development.
